Characterization of integrated crop-livestock-forest system in Brazil

### 2022-08-02 iclfs_review/lit_review.qmd
Change document style. Add more information about the review.

---
title: "Characterization of integrated crop-livestock-forest system in Brazil"
author: "Hugo Tameirão Seixas"
format: 
  html:
    page-layout: article
editor: visual
---

@@

@@

@@

>>>>

---
title: "Characterization of integrated crop-livestock-forest system in Brazil"
author: "Hugo Tameirão Seixas"
format: 
  html:
    page-layout: article
    toc: true
    toc-depth: 2
number-sections: true
---

@@

### Identify the review as a systematic review, meta-analysis, or both

This is a systematic review

### Summarise the aims and scope of the review

The main objective of this review is to synthesize data concerning ICLF in different aspects, creating an overview of the main characteristics of the ICLF being researched in Brazil. I will analyse variables such as above and below ground productivity of the tree, pasture and crop components; livestock productivity; system management characteristics; soil attributes; GHG emissions. I will evaluate national and international research conducted inside the Brazilian territory.

### Describe the data set

The data set will be composed by a collection of relational tables, each table will describe a characteristic of the ICLF in Brazil.

### State the results of the primary outcome

### State conclusions

### State limitations

@@

The review will be performed over any research that analysed any aspect of the ICLF in Brazil. Therefore this is a very general approach, which is feasible due to the limited amount of research in this topic. Only documents which are not explicitly about ICLF will be removed from the review.

I will extract data of a diverse number of variables, which will allow me to create an overview of the characteristics of the ICLF systems being analysed in Brazil.

@@

I have not yet identified any systematic review about ICLF in Brazil.
